Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Split the outcomes measured analysis into overall and top 6 per collab type

```{r}
outcomes_overall <- compact_data_with_citation_keys_no_fmd %>% 
  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
  separate_rows(outcome_measured, sep = ',') %>% 
  group_by(collab_type, outcome_measured) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  filter(!outcome_measured %in% c('outcome_other', '', 's')) %>% 
  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
  ungroup(outcome_measured) %>% 
  arrange(desc(num_of_studies), .by_group = TRUE) %>% 
  ungroup() %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(outcomes_overall, 
             caption = 'Outcomes studied by the collaboration types', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 
                                                    'HOLD_position', 
                                                    'repeat_header'), 
                                  font_size = 8)
```

>>>>

```{r}
outcomes_measured_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
  mutate(outcome_measured = str_trim(outcome_measured)) %>% 
  separate_rows(outcome_measured, sep = ',') %>% 
  group_by(collab_type, outcome_measured) %>% 
  distinct(title, .keep_all = TRUE) %>% 
  filter(!outcome_measured %in% c('outcome_other', '', 's')) %>% 
  count(collab_type, outcome_measured, name = 'num_of_studies') %>% 
  ungroup(outcome_measured) %>% 
  arrange(desc(num_of_studies), .by_group = TRUE)

knitr::kable(outcomes_measured_by_collab_type, 
             caption = 'Outcomes studied by the collaboration types', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 
                                                    'HOLD_position', 
                                                    'repeat_header')
                                  )
```

### Top 6 outcomes measured by collaboration type
```{r}
outcomes_measured_by_collab_type_top6 <- outcomes_measured_by_collab_type %>% 
  group_map(~ {
    .x %>% 
      adorn_totals() %>% 
      adorn_percentages(denominator = "col") %>%
      adorn_pct_formatting() %>%
      adorn_ns()},
    .keep = TRUE) %>% 
  map(head, n = 6) %>% 
  list_rbind()

knitr::kable(outcomes_measured_by_collab_type_top6, 
             caption = 'Top 6 outcomes studied by the collaboration types', 
             format = "latex", booktabs = TRUE, longtable = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 
                                                    'HOLD_position', 
                                                    'repeat_header')
                                  )
```
